---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Hunter Dacey"
date: "8/26/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

(Type your answer to Exercise 1 here. This exercise does not require any R code.)

### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

(Add code and narrative as needed. Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient. To finish, clean up the narrative by removing these instructions.)

Blah blah blah...

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()


```

I'm some text, you should replace me with more meaningful text...

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

There is more of a correlation with the datapoints for the star when company x vs y.

```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

There is less correlation whe it compares to other sets like Dino and Star.

```{r all_graph}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")

```

### Group By

Now we will use the group_by function to generate all the summary correlation coefficients.
``` {r group-by}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)

```